### 2012-03-28 contents.tex
Adding distribution of ratios (who).

		\caption{Discovered QA team for all four subprojects.} \label{tab:qa}
		\begin{tabular}{l|r|r}
			% \toprule
			\textbf{\centering Project} & 
			\textbf{\centering QA team size} & 
			\MyHead{1.5cm}{\textbf{\% of verifications by QA team}} \\
			\hline
			Eclipse & & \\
			\quad Platform        & 4 (2.4\%)  &  1.1\% \\
			\quad EMF             & 0 (0.0\%)  &  0.0\% \\
			NetBeans & & \\
			\quad Platform       & 25 (18.8\%) & 80.1\% \\
			\quad VersionControl & 5 (20.8\%) & 93.2\% \\
			% \bottomrule
		\end{tabular}
		\end{center}

@@

	Although the reported results are based on an arbitrary threshold (10) for the ratio between verifications and fixes, other values (2 and 5) were also used, leading to similar results.

>>>>

		\caption{Discovered QA team for all four subprojects.} \label{tab:qa}
		\begin{tabular}{l|r|r|c}
			% \toprule
			\textbf{\centering Project} & 
			\MyHead{1.2cm}{\textbf{\centering QA team size}} & 
			\MyHead{1.6cm}{\textbf{\% of verifications by QA team}} &
			\MyHead{2.7cm}{\textbf{Distribution of ratio (bugs verified / bugs fixed) per developer}} \\
			\hline
			\textbf{Eclipse} & & & 
			   \multirow{6}{*}{\includegraphics[scale=1]{ratio}}\\
			\quad Platform        & 4 (2.4\%)  &  1.1\% &  \\
			\quad EMF             & 0 (0.0\%)  &  0.0\% & \\
			\textbf{NetBeans} & & \\
			\quad Platform       & 25 (18.8\%) & 80.1\% & \\
			\quad V.Control & 5 (20.8\%) & 93.2\% & \\
			% \bottomrule
		\end{tabular}
		\end{center}

@@

	Although the reported results are based on an arbitrary threshold (10) for the ratio between verifications and fixes, other values (2 and 5) were also used, leading to similar results. The rightmost column of Table \ref{tab:qa} shows the distribution of the ratio, in log scale, where it can be seen that ratios above 10 are uncommon in all projects.
